---
title: "Happy Moments"
author: "Arpita Shah and Tian Zheng"
output: html_notebook
runtime: shiny
---

HappyDB is a corpus of 100,000 crowd-sourced happy moments via Amazon's Mechanical Turk. You can read more about it on https://arxiv.org/abs/1801.07746.

Here, we explore this data set and try to answer the question, "What makes people happy?"

### Step 0 - Load all the required libraries

From the packages' descriptions:

+ `tidyverse` is an opinionated collection of R packages designed for data science. All packages share an underlying design philosophy, grammar, and data structures;
+ `tidytext` allows text mining using 'dplyr', 'ggplot2', and other tidy tools;
+ `DT` provides an R interface to the JavaScript library DataTables;
+ `scales` map data to aesthetics, and provide methods for automatically determining breaks and labels for axes and legends;
+ `wordcloud2` provides an HTML5 interface to wordcloud for data visualization;
+ `gridExtra` contains miscellaneous functions for "grid" graphics;
+ `ngram` is for constructing n-grams (“tokenizing”), as well as generating new text based on the n-gram structure of a given text input (“babbling”);
+ `Shiny` is an R package that makes it easy to build interactive web apps straight from R;

```{r load libraries, warning=FALSE, message=FALSE}
library(tidyverse)
library(tidytext)
library(DT)
library(scales)
library(wordcloud2)
library(gridExtra)
library(ngram)
library(shiny) 
library(wordcloud)
```

### Step 1 - Load the processed text data along with demographic information on contributors

We use the processed data for our analysis and combine it with the demographic information available.

```{r load data, warning=FALSE, message=FALSE}
hm_data <- read_csv("../output/processed_moments.csv")

urlfile<-'https://raw.githubusercontent.com/rit-public/HappyDB/master/happydb/data/demographic.csv'
demo_data <- read_csv(urlfile)
```

### Combine both the data sets and keep the required columns for analysis

We select a subset of the data that satisfies specific row conditions.

```{r combining data, warning=FALSE, message=FALSE}
hm_data <- hm_data %>%
  inner_join(demo_data, by = "wid") %>%
  select(wid,
         original_hm,
         gender, 
         marital, 
         parenthood,
         reflection_period,
         age, 
         country, 
         ground_truth_category, 
         text) %>%
  mutate(count = sapply(hm_data$text, wordcount)) %>%
  filter(gender %in% c("m", "f")) %>%
  filter(marital %in% c("single", "married")) %>%
  filter(parenthood %in% c("n", "y")) %>%
  filter(reflection_period %in% c("24h", "3m")) %>%
  mutate(reflection_period = fct_recode(reflection_period, 
                                        months_3 = "3m", hours_24 = "24h"))
```

```{r}
datatable(hm_data)
```
# Level I: Simple wordcloud analysis

As a graduate student who are in their early 20s, we are interested in what will make us happy when we are in our 30s. More specifically, we want to see what is the difference between our 20s and 30s when we further diversify the sample into gender and parenthood. Here are some sample questions that we wish to answer after finishing our analysis:
1. What makes us happy 20s vs. 30s?
2. What makes us happy 20s(parenthood) vs. 30s(parenthood)?
3. What makes us happy 20s (male) vs. 30s (male)?

```{r}
hm_data$num_age <-as.numeric(hm_data$age)
hm_data<-hm_data[is.na(hm_data$num_age)!=T,]
age_between_20_30 <- hm_data[hm_data$num_age>=20&hm_data$num_age<30,]
age_between_30_40 <- hm_data[hm_data$num_age>=30&hm_data$num_age<40,]
```

### Create a bag of words using the text data

```{r bag of words, warning=FALSE, message=FALSE}
bag_of_words <-  hm_data %>%
  unnest_tokens(word, text)
word_count <- bag_of_words %>%
  count(word, sort = TRUE)

word_age_between_20_30 <-age_between_20_30 %>%
  unnest_tokens(word, text)
word_count_age_between_20_30 <- word_age_between_20_30 %>%
  count(word,sort = TRUE)

word_age_between_30_40 <-age_between_30_40 %>%
  unnest_tokens(word, text)
word_count_age_between_30_40 <- word_age_between_30_40 %>%
  count(word,sort = TRUE)
```

```{r}
wordcloud(words=word_count_age_between_20_30$word,freq=word_count_age_between_20_30$n,
           min.freq=10, max.words= 100, random.order = F, rot.per = .35, colors = brewer.pal(8,"Dark2"))

wordcloud(words=word_count_age_between_30_40$word,freq=word_count_age_between_30_40$n,
           min.freq=10, max.words= 100, random.order = F, rot.per = .35, colors = brewer.pal(8,"Dark2"))
```

As we can see from the wordcloud that for people in their 20s, friend/day/time are most frequent things showing up in the survey. And the other more frequent things are game/birthday/enjoyed/fun. While as for people in their 30s, once again, day/friend/time are most frequent. However, the other more frequent things are a bit different whic are home/family/son/wife/feel/fun...From the output we can infer when people aging from 20 to 30ish, their concentrations of life shift to family yet things make them happy in their 20s are still playing an important role in their lifef making them happy.

```{r}
age_between_20_30_parenthood <- age_between_20_30[age_between_20_30$parenthood=="y",]
age_between_30_40_parenthood <- age_between_30_40[age_between_30_40$parenthood=="y",]
```

### Create a bag of words using the text data

```{r bag of words, warning=FALSE, message=FALSE}
bag_of_words <-  hm_data %>%
  unnest_tokens(word, text)
word_count <- bag_of_words %>%
  count(word, sort = TRUE)

word_age_between_20_30_parenthood <-age_between_20_30_parenthood %>%
  unnest_tokens(word, text)
word_count_age_between_20_30_parenthood <- word_age_between_20_30_parenthood %>%
  count(word,sort = TRUE)

word_age_between_30_40_parenthood <-age_between_30_40_parenthood %>%
  unnest_tokens(word, text)
word_count_age_between_30_40_parenthood <- word_age_between_30_40_parenthood %>%
  count(word,sort = TRUE)
```

```{r}
wordcloud(words=word_age_between_20_30_parenthood$word,freq=word_count_age_between_20_30_parenthood$n,
           min.freq=10, max.words= 100, random.order = F, rot.per = .35, colors = brewer.pal(8,"Dark2"))

wordcloud(words=word_count_age_between_30_40_parenthood$word,freq=word_count_age_between_30_40_parenthood$n,
           min.freq=10, max.words= 100, random.order = F, rot.per = .35, colors = brewer.pal(8,"Dark2"))
```
As we can see for people in their 20s with parenthood, what makes them happy is something like son/movie/fun/run/time which is not too different from those without parenthood. Maybe is because they are new parents? Or maybe they are just beginning learning how to be a great parent?

In contrast, for people in their 30s with parenthood, they are more mature folks. What makes them happy is somehing like Son/family/husband/wife/life/kids. They are more family oriented. It makes sense because after years training/practice to be great parent, being family oriented is an important factor that should be attributed to. 

In addition, I have to point out that there might be some bias in the sample which can be explained properly. For example, anger makes people happy? This does not make any sense generally.

```{r}
age_between_20_30_male <- age_between_20_30[age_between_20_30$gender=="m",]
age_between_30_40_male <- age_between_30_40[age_between_30_40$gender=="m",]
```

### Create a bag of words using the text data

```{r bag of words, warning=FALSE, message=FALSE}
bag_of_words <-  hm_data %>%
  unnest_tokens(word, text)
word_count <- bag_of_words %>%
  count(word, sort = TRUE)

word_age_between_20_30_male <-age_between_20_30_male %>%
  unnest_tokens(word, text)
word_count_age_between_20_30_male <- word_age_between_20_30_male %>%
  count(word,sort = TRUE)

word_age_between_30_40_male <-age_between_30_40_male %>%
  unnest_tokens(word, text)
word_count_age_between_30_40_male <- word_age_between_30_40_male %>%
  count(word,sort = TRUE)
```

```{r}
wordcloud(words=word_age_between_20_30_male$word,freq=word_count_age_between_20_30_male$n,
           min.freq=10, max.words= 100, random.order = F, rot.per = .35, colors = brewer.pal(8,"Dark2"))

wordcloud(words=word_count_age_between_30_40_male$word,freq=word_count_age_between_30_40_male$n,
           min.freq=10, max.words= 100, random.order = F, rot.per = .35, colors = brewer.pal(8,"Dark2"))
```
For people like me who are in their 20s and are male, what makes them happy is something like examination/birthday/night/girl:) This is not a surprise for me. However,what surprises me is that son is the most frequent word here. As a result, I certainly doubt the sample or the result since this is a bit weird for a society that is considered having gender equality.

Well, things will change when we (male in 20s) turn to our 30s. We will become more reliable gentlemen. What makes us happy is friend/family/home...I look forward getting aged to some extend based on the output.

# Level II: Sentiment Analysis

```{r}
age_between_20_30%>%
  unnest_tokens(word, text)%>%
  select(word)%>%
  inner_join(get_sentiments("nrc"))%>%
  count(word,sentiment, sort=T)%>%
  ungroup()%>%
  group_by(sentiment)%>%
  top_n(10)%>%
  ungroup()%>%
  mutate(word=reorder(word, n))%>%
  ggplot(aes(word, n, fill=sentiment))+
  geom_col(show.legend = F)+
  facet_wrap(~sentiment,scales = "free_y")+
  labs(y="conttribution", 
       x=NULL)+
  coord_flip()

age_between_30_40%>%
  unnest_tokens(word, text)%>%
  select(word)%>%
  inner_join(get_sentiments("nrc"))%>%
  count(word,sentiment, sort=T)%>%
  ungroup()%>%
  group_by(sentiment)%>%
  top_n(10)%>%
  ungroup()%>%
  mutate(word=reorder(word, n))%>%
  ggplot(aes(word, n, fill=sentiment))+
  geom_col(show.legend = F)+
  facet_wrap(~sentiment,scales = "free_y")+
  labs(y="conttribution", 
       x=NULL)+
  coord_flip()
```
# from the sentiment analysis we can see that people who are older (30s) have less fear emotion and more joy emotion than people who are in their 20s. It might be attributed to as people getting more sophisticated they can better distinguish joy between fear. However, we notice that for the same word "money", elder people tend to be anger on it. Maybe it is because people realize money is evil? But if we spell back evil, it is live...That's a bonus finding:)

# Level III: Topic Modelling 

```{r}
happy.moment=read.csv("../output/processed_moments.csv", stringsAsFactors = FALSE)
demographic=read.csv("../data/demographic.csv")
senselabel=read.csv("../data/senselabel.csv")
Happy.text <- happy.moment$text
Happy.text <- happy.moment$text
docs <- Corpus(VectorSource(Happy.text))
dtm <- DocumentTermMatrix(docs)
rowTotals <- slam::row_sums(dtm) #Find the sum of words in each Document
dtm <- dtm[rowTotals> 0, ]
happy.moment <- happy.moment[rowTotals> 0, ]

#####Topic Modelling by the LDA method#####

burnin <- 4000
iter <- 2000
thin <- 500
seed <-list(2003,5,63,100001,765)
nstart <- 5
best <- TRUE

#Number of topics
k <- 10

#Run LDA using Gibbs sampling
ldaOut <-LDA(dtm, k, method="Gibbs", control=list(nstart=nstart, 
                                                 seed = seed, best=best,
                                                 burnin = burnin, iter = iter, 
                                                 thin=thin))
#write out results
#docs to topics
ldaOut.topics <- as.matrix(topics(ldaOut))
table(c(1:k, ldaOut.topics))
write.csv(ldaOut.topics,file=paste("../output/LDAGibbs",k,"DocsToTopics.csv"))

#top 6 terms in each topic
ldaOut.terms <- as.matrix(terms(ldaOut,20))
write.csv(ldaOut.terms,file=paste("../output/LDAGibbs",k,"TopicsToTerms.csv"))

#probabilities associated with each topic assignment
topicProbabilities <- as.data.frame(ldaOut@gamma)
write.csv(topicProbabilities,file=paste("../output/LDAGibbs",k,"TopicProbabilities.csv"))


terms.beta=ldaOut@beta
terms.beta=scale(terms.beta)
topics.terms=NULL
for(i in 1:k){
  topics.terms=rbind(topics.terms, ldaOut@terms[order(terms.beta[i,], decreasing = TRUE)[1:60]])
}

for(i in 1:k){
  topics.terms=rbind(topics.terms, ldaOut@terms[order(terms.beta[i,], decreasing = TRUE)[1:60]])
}

#par(mfrow = c(5, 2), mar = c(1,1,2,0), bty = "n", xaxt = "n", yaxt = "n")
# visualize topics as word cloud
for (i in c(2,3,4,6,8,9,10)) {
  topicToViz <- i
# select to 40 most probable terms from the topic by sorting the term-topic-probability vector in decreasing order
  top40terms <- topics.terms[i,]
# extract the probabilites of each of the 40 terms
  hm_results <- posterior(ldaOut)
  probabilities <- sort(hm_results$terms[topicToViz,], decreasing=TRUE)[1:60]
# visualize the terms as wordcloud
  mycolors <- brewer.pal(8, "Dark2")
  wordcloud(top40terms, probabilities, random.order = FALSE, color = mycolors)
}

#topics.terms
ldaOut.terms
```
As we can see from the output, the hottest 10 topics from Happy Moment dataset can be categorized into "found", "day", "time", "morning", "feel", "dinner", "friend","watched"    "finally", and "walk".   

### Create bigrams using the text data

```{r bigram, warning=FALSE, message=FALSE}
hm_bigrams <- hm_data %>%
  filter(count != 1) %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2)

bigram_counts <- hm_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  count(word1, word2, sort = TRUE)
```

### Specify the user interface for the R Shiny app

We want each tab to have its own controls for input and so Shiny's "navbarPage()" layout works the best. We have the first tab visualizing the overall data, second one for scatterplots comparing the proportion of words within categories, third one highlighting the most frequently appearing bigrams based on categories and the last tab to explore the actual happy moments.

```{r shiny UI, warning=FALSE, message=FALSE}
ui <- navbarPage("What makes people happy?",
                 tabPanel("Overview",
                          
                          titlePanel(h1("Most Frequent Occurrences",
                                        align = "center")),
                          
                          sidebarLayout(
                            sidebarPanel(
                              sliderInput(inputId = "topWordcloud",
                                          label = "Number of terms for word cloud:",
                                          min = 5,
                                          max = 100,
                                          value = 50),
                              br(),
                              br(),
                              
                              checkboxInput(inputId = "topFreqB",
                                            label = "Plot Bar Chart",
                                            value = F),
                              sliderInput(inputId = "topBarchart",
                                          label = "Number of terms for bar chart:",
                                          min = 1,
                                          max = 25,
                                          value = 10),
                              br(),
                              br(),
                              
                              checkboxInput(inputId = "topFreqN",
                                            label = "Plot Network Graph",
                                            value = F),
                              sliderInput(inputId = "topNetwork",
                                          label = "Number of edges for network graph:",
                                          min = 1,
                                          max = 150,
                                          value = 50)
                            ),
                            
                            mainPanel(
                              wordcloud2Output(outputId = "WC"),
                              plotOutput(outputId = "figure")
                            )
                          )
                 ),
                 
                 tabPanel("Individual Terms",
                          
                          titlePanel(h1("Comparison of Proportions",
                                        align = "center")),
                          
                          sidebarLayout(
                            sidebarPanel(
                              selectInput(inputId = "attribute",
                                          label = "Select the attribute:",
                                          choices = c("Gender" = "gender",
                                                      "Marital Status" = "marital",
                                                      "Parenthood" = "parenthood",
                                                      "Reflection Period" = "reflection_period")
                              )
                            ),
                            
                            mainPanel(
                              plotOutput(outputId = "scatter")
                            )
                          )
                 ),
                 
                 tabPanel("Pair of Words",
                          
                          titlePanel(h1("Most Frequent Bigrams",
                                        align = "center")),
                          
                          sidebarLayout(
                            sidebarPanel(
                              selectInput(inputId = "factor",
                                          label = "Select the attribute:",
                                          choices = c("Gender" = "gender",
                                                      "Marital Status" = "marital",
                                                      "Parenthood" = "parenthood",
                                                      "Reflection Period" = "reflection_period")
                              ),
                              numericInput(inputId = "topBigrams",
                                          label = "Number of top pairs to view:",
                                          min = 1,
                                          max = 25,
                                          value = 10)
                            ),
                            
                            mainPanel(
                              plotOutput(outputId = "bar")
                            )
                          )
                 ),
                 
                 tabPanel("Data",
                          DT::dataTableOutput("table")
                          )
)
```

### Develop the server for the R Shiny app

This shiny app visualizes summary of data and displays the data table itself.

```{r shiny server, warning=FALSE, message=FALSE}
server <- function(input, output, session) {
  
  pt1 <- reactive({
    if(!input$topFreqB) return(NULL)
    word_count %>%
      slice(1:input$topBarchart) %>%
      mutate(word = reorder(word, n)) %>%
      ggplot(aes(word, n)) +
      geom_col() +
      xlab(NULL) +
      ylab("Word Frequency")+
      coord_flip()
  })
  
  pt2 <- reactive({
    if(!input$topFreqN) return(NULL)
    bigram_graph <- bigram_counts %>%
      slice(1:input$topNetwork) %>%
      graph_from_data_frame()
    
    set.seed(123)
    
    x <- grid::arrow(type = "closed", length = unit(.1, "inches"))
    
    ggraph(bigram_graph, layout = "fr") +
      geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                     arrow = x, end_cap = circle(.05, 'inches')) +
      geom_node_point(color = "skyblue", size = 3) +
      geom_node_text(aes(label = name), repel = TRUE) +
      theme_void()
  })
  
  output$WC <- renderWordcloud2({
    
    word_count %>%
      slice(1:input$topWordcloud) %>%
      wordcloud2(size = 0.6,
                 rotateRatio = 0)
    
  })
  
  output$figure <- renderPlot(height = 500, width = 500, {
    
    ptlist <- list(pt1(),pt2())
    ptlist <- ptlist[!sapply(ptlist, is.null)]
    if(length(ptlist)==0) return(NULL)
    
    lay <- rbind(c(1,1),
                 c(2,2))
    
    grid.arrange(grobs = ptlist, layout_matrix = lay)
  })
  
  
  
  selectedAttribute <- reactive({
    list(atr = input$attribute)
  })
  
  output$scatter <- renderPlot({
    temp <- bag_of_words %>%
      count(!!as.name(selectedAttribute()$atr), word) %>%
      group_by(!!as.name(selectedAttribute()$atr)) %>%
      mutate(proportion = n / sum(n)) %>% 
      select(-n) %>% 
      spread(!!as.name(selectedAttribute()$atr), proportion)
    
      ggplot(temp, 
             aes_string(x = colnames(temp)[2], y = colnames(temp)[3]),
             color = abs(colnames(temp)[3] - colnames(temp)[2])) +
      geom_abline(color = "gray40", lty = 2) +
      geom_jitter(alpha = 0.1, size = 1, width = 0.3, height = 0.3) +
      geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
      scale_x_log10(labels = percent_format()) +
      scale_y_log10(labels = percent_format()) +
      scale_color_gradient(limits = c(0, 0.001), low = "darkslategray4", high = "gray75") +
      theme(legend.position="none")
  })
  
  
  
  selectedBigram <- reactive({
    list(var = input$factor)
  })
  
  output$bar <- renderPlot({
    hm_bigrams %>%
      count(!!as.name(selectedBigram()$var), bigram, sort = TRUE) %>%
      group_by(!!as.name(selectedBigram()$var)) %>%
      top_n(input$topBigrams) %>%
      ungroup() %>%
      mutate(bigram = reorder(bigram, n)) %>%
      ggplot(aes(bigram, n, fill = !!as.name(selectedBigram()$var))) +
      geom_col(show.legend = FALSE) +
      facet_wrap(as.formula(paste("~", selectedBigram()$var)), ncol = 2, scales = "free") +
      coord_flip()
  })
  
  
  output$table <- DT::renderDataTable({
    DT::datatable(hm_data)
  })
}
```

### Run the R Shiny app

```{r shiny app, warning=FALSE, message=FALSE}
shinyApp(ui, server)
```
